---
title: "The Linreg Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The Linreg Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  options(width = 150),
  fig.align = 'center',
  comment = "#>"
)
```
This vignette summarizes the package `linreg` and all its dependent methods. To use the package, run the command below :
```{r setup}
library(advancedRLab4)
```

## Linreg

The function `linreg` takes two arguments, `formula` and `data`, where `data` is a data.frame. The example below utilises the `iris` data.frame.The `linreg` function, uses QR decomposition to calculate the values listed below and store them in an object of class "`linreg`" and return this object.


```{r}
data(iris)
mod_object <- linreg(formula = Petal.Length ~ Species, data = iris)
print(names(mod_object))
```
The object `linreg` contains the following elements

* QR          <- object of type qr
* Q           <- the matrix `Q`
* R           <- the triangular matrix `R`
* varB        <- variance of  $\hat{\beta}$
* ehat        <- residual values $\hat{e}$
* y_fitted    <- the fitted values $\hat{y}$
* Beta        <- regression coefficients $\beta$
* dof         <- Degrees of freedom
* tval        <- t-values
* pval        <- p-values
* sigma1      <- standard deviation $\sigma$ 
* stde        <- Standard Error
* formula     <- the input `formula` object
* dfname      <- name of the input data.frame

## Functions 
 
### print()

This is an S3 Method implementation of the generic `print` function, which prints out the coefficient and coefficient names as well the function call. See example below : 
```{r}
print(mod_object)
```

### plot()

The `plot` function is an S3 Method implementation of the generic `plot` function. It plots two graphs : 
```{r}
plot(mod_object)
```

1. Residual Values vs Fitted Values
2. $\sqrt{StandardizedResiduals}$ vs Fitted Values

### resid()

This is an S3 Method. It returns the residuals calculated.
```{r}
head(resid(mod_object))
```

### pred()

This function return the predicted values $\hat{y}$
```{r}
head(pred(mod_object))
```

### coef()

This function returns the coefficients as named vector.
```{r}
coef(mod_object)
```

### summary()

This functions summarizes the coefficients with their standard error, t-values, p-values, estimated $\hat{\sigma}$ and the degrees of freedom in the model.

```{r}
summary(mod_object)
```
